\chapter{Literature Review}
\label{Chapter2}
\lhead{Chapter 2. \emph{Literature Review}}

\section{What is Optimization?}
\subsection{Definition and Concept}
Discuss the general concept of optimization, emphasizing its role in operations research and decision-making, and explaining how it aims to find the most favorable solution from available alternatives.

\subsection{Exact vs. Heuristic Methods}
\textbf{Exact Methods:} Describe methods that provide guaranteed optimal solutions, such as linear programming and integer programming.
\textbf{Heuristic Methods:} Introduce heuristic approaches, like genetic algorithms and simulated annealing, used in complex problems where exact solutions are computationally impractical.
\textbf{Comparison:} Analyze the trade-offs between exactness and computational efficiency.

\subsection{Day-to-Day Optimization Examples}
Illustrate how optimization is applied in everyday scenarios such as route planning, airline scheduling, and personal time management.

\section{Building Blocks for Monte Carlo Tree Search}
\subsection{Markov Chains}
Introduce the theory of Markov Chains and their application in modeling stochastic processes and optimization.
\subsection{Monte Carlo Methods}
Discuss the basics of Monte Carlo methods, focusing on their use in solving complex computational problems through random sampling.

\section{Monte Carlo Tree Search}
Detailed discussion on Monte Carlo Tree Search (MCTS), explaining how it extends Monte Carlo methods to decision-making problems, particularly highlighting its relevance in AI and game theory.
Do different part to highlight the differents plociies, the different parameters - how it has been used especially in game theory and so on

\section{Monte Carlo Tree Search in Routing Optimization}
\subsection{Overview of Routing Challenges}
Present an overview of different routing problems, including the Traveling Salesman Problem and the Vehicle Routing Problem, focusing on their complexities and the optimization strategies employed.
\subsection{Application to Kiwi.com Problem}
Discuss the specific application of MCTS to the Kiwi.com challenge, including how the unique properties of the problem are addressed by this method.

\section{Review of Previous Approaches to the Kiwi.com Problem}
\subsection{Survey of Approaches}
Discuss main approaches like Local Search Algorithms, Reinforcement Learning, and Genetic Algorithms, mentioning key studies that have tackled similar challenges.
\textbf{Local Search Algorithms:} Explore the principles and applications of Local Search, highlighting specific papers and their results.
\textbf{Reinforcement Learning:} Review the application of Reinforcement Learning in transportation optimization, citing relevant studies.
\textbf{Genetic Algorithms:} Describe how Genetic Algorithms have been used to solve complex routing problems and their effectiveness in various scenarios.
\subsection{Comparative Analysis}
Provide a comparative analysis of these methods with Monte Carlo Tree Search, evaluating performance under different conditions based on the nature of the problem.

\section{Research Motivation and Literature Gaps}
\subsection{Motivation for This Study}
Discuss the motivations for using MCTS in solving the Kiwi.com problem, considering the problem’s complexity and scale.
\subsection{Identification of Gaps}
Highlight areas not fully explored by previous studies, such as scalability or real-time application constraints, emphasizing the novel aspects of your research.

\section{Critical Analysis of Existing Research}
Analyze the strengths and weaknesses of the studies reviewed, providing a critical perspective in relation to your research. Discuss how convincing the authors' arguments are and where your research might offer improved or alternative solutions.

\todo{Further refine and expand sections based on feedback and ongoing research.}