\addtotoc{Abstract}

\abstract{\addtocontents{toc}{\vspace{1em}}

    %    \todo{Give a short (1 page) overview of the work. This should summarise (not advertise) your research project. After reading the abstract the reader should know what problem you are tackling, the techniques you are using, the results you have achieved.}
}

This dissertation addresses the challenge posed by Kiwi.com, the Traveling Salesman problem 2.0. Despite some similarities with the classic Traveling Salesman Problem
(TSP), the problem is more complex. It can be characterised as an asymmetric, time-
constrained and generalised TSP. Moreover, infeasibility adds further complexity as
there are no ﬂights available between speciﬁc airports at speciﬁc days. Exact methods
often fail in solving these $\mathcal{NP}$-Hard problems. Therefore, alternative approaches, such
as heuristics, are preferred to face these cases. A Monte Carlo Tree Search (MCTS)
was implemented to tackle Kiwi’s challenge, an algorithm traditionnaly used in board
games, but here adapted to solve an air travel optimisation problem.

The focus of this paper is on the first eight instances of the problem, without taking into
account the time constraints set by Kiwi.com. The MCTS has been chosen for its proven
efectiveness in handling complex and high dimensionnal search spaces, therefore well
suited for this modified TSP. The most notable results of the thesis include the successful
implementation of Monte Carlo Tree Search (MCTS) to solve six out of eight problem
instances, achieving results that match or closely approximate the best-known solutions.
One new best solution have been found for instance eight. A thorough analysis of the
algorithm’s parameters, such as the selection, expansion, simulation and parralelisation
policies have been conducted, providing insights into their influence on the algorithm’s
performance. It is recommended to implement MCTS using a greedy simulation policy
and UCB1-Tuned selection policy for smaller instances, while employing UCB for more
complex scenarios. Regarding the expansion policy, the top k function found better
solutions accross all instances. Furthermore, a five cores leaf parrelisation is to consider
when using stochastic simulation policies. All these parameters guide eciently the tree
search towards the best solutions.
\\
\\
\textit{Keywords: Optimisation, Travelling Salesman Problem, Monte Carlo Tree Search, Air
Travel Optimisation.}

\clearpage

